### 2014-02-22 paper/retrofit.tex
fold in the eval ctx in ml

\begin{mathpar}
\and
\inferrule[T-pure]
{| te ~> te'|}
{| conf tS (intE te) -> conf tS (intE te') |}

\and
\inferrule[T-app]
{ } {| (\x.te) tv ~> {tv/x} te |}

\and
\inferrule[T-ifTrue]
{ } {| if true then te1 else te2  ~> te1|}

\and
\inferrule[T-ifFalse]
{ } {| if false then te1 else te2  ~> te2|}

\and
\inferrule[T-ref]
{| tS' = tS [ ta mapsto tv ] | } 
{| conf tS (intE (ref tv)) -> conf tS' (intE ta) |}
{| fresh (ta) |}

\and
\inferrule[T-deref]
{| tv = tS(ta) |}
{| conf tS (intE (!ta)) -> conf tS (intE tv) |}

\and
\inferrule[T-ass]
{| tS' = tS [ ta mapsto tv ] |} 
{| conf tS (intE (ta := tv)) -> conf tS' (intE tv) |}
\end{mathpar}

@@

\begin{itemize}
\item Label transition systems.
\item Arbitrary scheduling policies $\alpha$
\end{itemize}

>>>>

\begin{mathpar}
\and
\inferrule[T-evalCtx]
{| conf tS te -> conf tS' te')|}
{| conf tS (intE te) -> conf tS' (intE te') |}

\and
\inferrule[T-app]
{ } {| conf tS ((\x.te) tv) ~> conf tS ({tv/x} te) |}

\and
\inferrule[T-ifTrue]
{ } {| conf tS (if true then te1 else te2)  ~> conf tS te1|}

\and
\inferrule[T-ifFalse]
{ } {| conf tS (if false then te1 else te2)  ~> conf tS te2|}

\and
\inferrule[T-ref]
{| tS' = tS [ ta mapsto tv ] | } 
{| conf tS (ref tv) -> conf tS' ta |}
{| fresh (ta) |}

\and
\inferrule[T-deref]
{| tv = tS(ta) |}
{| conf tS (!ta) -> conf tS tv |}

\and
\inferrule[T-ass]
{| tS' = tS [ ta mapsto tv ] |} 
{| conf tS (ta := tv) -> conf tS' tv |}
\end{mathpar}

@@

\begin{itemize}
\item Label transition systems.
\item Non-deterministic reduction.
\item Arbitrary scheduling policies $\alpha$
\end{itemize}
